\textbf{Supplementary Information}

### 2020-11-19 submission/supplementary.tex
Format customization.

\hypertarget{supplementary-figures}{%
\subsection{Supplementary Figures}\label{supplementary-figures}}

@@

\hypertarget{supplementary-table}{%
\subsection{Supplementary Table}\label{supplementary-table}}

@@

\begin{longtable}[t]{>{\centering\arraybackslash}p{5em}ccccccccc}
\caption{\label{tab:metagenomic_statistics}Sample ID, sampling station, community type, sampling date, number of raw sequence pairs, number of assembled contigs by MEGAHIT, N50 and L50 assembly statistics, number of predicted coding sequences (CDS) by Prodigal and number of eggNOGmapper annotated CDS.\label{metagenomic_statistics}}\\
\toprule
\textbf{Sample ID} & \textbf{Station} & \textbf{Community Type} & \textbf{Date} & \textbf{\makecell[c]{No. of Raw\\Sequence Pairs}} & \textbf{\makecell[c]{No. of\\Contigs}} & \textbf{N50\textsuperscript{*}} & \textbf{L50 (bp)\textsuperscript{*}} & \textbf{\makecell[c]{No. of\\Predicted\\CDS}} & \textbf{\makecell[c]{No. of\\Annotated\\CDS}}\\
\midrule
\endfirsthead
\caption[]{Sample ID, sampling station, community type, sampling date, number of raw sequence pairs, number of assembled contigs by MEGAHIT, N50 and L50 assembly statistics, number of predicted coding sequences (CDS) by Prodigal and number of eggNOGmapper annotated CDS.\label{metagenomic_statistics} \textit{(continued)}}\\
\toprule
\textbf{Sample ID} & \textbf{Station} & \textbf{Community Type} & \textbf{Date} & \textbf{\makecell[c]{No. of Raw\\Sequence Pairs}} & \textbf{\makecell[c]{No. of\\Contigs}} & \textbf{N50\textsuperscript{*}} & \textbf{L50 (bp)\textsuperscript{*}} & \textbf{\makecell[c]{No. of\\Predicted\\CDS}} & \textbf{\makecell[c]{No. of\\Annotated\\CDS}}\\
\midrule
\endhead
\
\endfoot
\bottomrule
\multicolumn{10}{l}{\textsuperscript{*} The notation was preserved from the original output of BBTools stats.sh.}\\
\endlastfoot
45 & Funtana & \textit{Cymodocea nodosa} (Mixed) & 14 December 2017 & 288,446,922 & 10,786,127 & 1,814,108 & 1,011 & 15,230,601 & 9,066,667\\
47 & Funtana & \textit{Caulerpa cylindracea} (Monospecific) & 14 December 2017 & 207,149,524 & 14,541,483 & 3,417,214 & 684 & 19,415,048 & 12,179,801\\
61 & Funtana & \textit{Cymodocea nodosa} (Mixed) & 19 June 2018 & 624,029,930 & 25,843,073 & 5,036,213 & 873 & 35,296,634 & 20,256,215\\
63 & Funtana & \textit{Caulerpa cylindracea} (Monospecific) & 19 June 2018 & 241,132,752 & 15,909,915 & 4,071,946 & 654 & 20,643,084 & 13,064,686\\*
\end{longtable}
\endgroup{}

@@

\caption{\label{tab:metagenomic_taxonomy}Phyla into which CDS were classifed, number and proportion of CDS in different phyla and sum of coding sequences' RPKM (Reads Per Kilobase Million) and their proportion in different phyla. Data are derived from sequenced metagenomes. Each metagenomic sample is labeled with sampling station, community type, sampling date and sample ID. For each sample top ten phyla based on RPKM were selected. CDS that were not successfully classified were excluded from the dataset.\label{metagenomic_taxonomy}}\\

@@

\caption[]{Phyla into which CDS were classifed, number and proportion of CDS in different phyla and sum of coding sequences' RPKM (Reads Per Kilobase Million) and their proportion in different phyla. Data are derived from sequenced metagenomes. Each metagenomic sample is labeled with sampling station, community type, sampling date and sample ID. For each sample top ten phyla based on RPKM were selected. CDS that were not successfully classified were excluded from the dataset.\label{metagenomic_taxonomy} \textit{(continued)}}\\

>>>>

\hypertarget{supplementary-figure}{%
\subsection{Supplementary figure}\label{supplementary-figure}}

@@

\hypertarget{supplementary-tables}{%
\subsection{Supplementary tables}\label{supplementary-tables}}

@@

\begin{longtable}[t]{>{\centering\arraybackslash}p{5em}ccccccccc}
\caption{\label{tab:metagenomic_statistics}Sample ID, sampling station, community type, sampling date, number of raw sequence pairs, number of assembled contigs by MEGAHIT, N50 and L50 assembly statistics, number of predicted coding sequences (CDS) by Prodigal and number of eggNOG-mapper annotated CDS.\label{metagenomic_statistics}}\\
\toprule
\textbf{Sample ID} & \textbf{Station} & \textbf{Community Type} & \textbf{Date} & \textbf{\makecell[c]{No. of Raw\\Sequence Pairs}} & \textbf{\makecell[c]{No. of\\Contigs}} & \textbf{N50\textsuperscript{*}} & \textbf{L50 (bp)\textsuperscript{*}} & \textbf{\makecell[c]{No. of\\Predicted\\CDS}} & \textbf{\makecell[c]{No. of\\Annotated\\CDS}}\\
\midrule
\endfirsthead
\caption[]{Sample ID, sampling station, community type, sampling date, number of raw sequence pairs, number of assembled contigs by MEGAHIT, N50 and L50 assembly statistics, number of predicted coding sequences (CDS) by Prodigal and number of eggNOG-mapper annotated CDS.\label{metagenomic_statistics} \textit{(continued)}}\\
\toprule
\textbf{Sample ID} & \textbf{Station} & \textbf{Community Type} & \textbf{Date} & \textbf{\makecell[c]{No. of Raw\\Sequence Pairs}} & \textbf{\makecell[c]{No. of\\Contigs}} & \textbf{N50\textsuperscript{*}} & \textbf{L50 (bp)\textsuperscript{*}} & \textbf{\makecell[c]{No. of\\Predicted\\CDS}} & \textbf{\makecell[c]{No. of\\Annotated\\CDS}}\\
\midrule
\endhead
\
\endfoot
\bottomrule
\multicolumn{10}{l}{\textsuperscript{*} The notation was preserved from the original output of BBTools stats.sh.}\\
\endlastfoot
45 & Funtana & \textit{Cymodocea nodosa} (Mixed) & 14 December 2017 & 288,446,922 & 10,786,127 & 1,814,108 & 1,011 & 15,230,601 & 9,066,667\\
47 & Funtana & \textit{Caulerpa cylindracea} (Monospecific) & 14 December 2017 & 207,149,524 & 14,541,483 & 3,417,214 & 684 & 19,415,048 & 12,179,801\\
61 & Funtana & \textit{Cymodocea nodosa} (Mixed) & 19 June 2018 & 624,029,930 & 25,843,073 & 5,036,213 & 873 & 35,296,634 & 20,256,215\\
63 & Funtana & \textit{Caulerpa cylindracea} (Monospecific) & 19 June 2018 & 241,132,752 & 15,909,915 & 4,071,946 & 654 & 20,643,084 & 13,064,686\\*
\end{longtable}
\endgroup{}

@@

\caption{\label{tab:metagenomic_taxonomy}Phyla into which CDS were classified, number and proportion of CDS in different phyla and sum of coding sequences' RPKM (Reads Per Kilobase Million) and their proportion in different phyla. Data are derived from sequenced metagenomes. Each metagenomic sample is labelled with sampling station, community type, sampling date and sample ID. For each sample top ten phyla based on RPKM were selected. CDS that were not successfully classified were excluded from the dataset.\label{metagenomic_taxonomy}}\\

@@

\caption[]{Phyla into which CDS were classified, number and proportion of CDS in different phyla and sum of coding sequences' RPKM (Reads Per Kilobase Million) and their proportion in different phyla. Data are derived from sequenced metagenomes. Each metagenomic sample is labelled with sampling station, community type, sampling date and sample ID. For each sample top ten phyla based on RPKM were selected. CDS that were not successfully classified were excluded from the dataset.\label{metagenomic_taxonomy} \textit{(continued)}}\\
